\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-01 paper/main.tex
added flow chart figure
fixes and cleanup in impact section

@@

Like virtual environments, containers, and virtual machines, the
\texttt{davos} library (when used in conjunction with Jupyter
notebooks) provides a lightweight mechanism for sharing code and
ensuring reproducibility across users and computing environments
(Fig.~\ref{fig:code-sharing}). Further, \texttt{davos} enables users
to fully specify (and install, as needed) any project dependencies
within the same notebook. This provides a system whereby executable
code (along with text and media) \textit{and} code for setting up and
configuring the project dependencies, may be combined within a single
notebook file.

We designed \texttt{davos} for use in research applications. For
example, in many settings \texttt{davos} may be used as a drop-in
replacement for more-difficult-to-set-up virtual environments,
containers, and/or virtual machines. For researchers, this lowers
barriers to sharing code. By eliminating most of the setup costs
of reconstructing the original researchers' computing environment,
\texttt{davos} also lowers barriers to entry for members of
the scientific community and the public who seek to \textit{benefit}
from shared code.

Beyond research applications, \texttt{davos} is also useful in
pedagogical settings. For example, in programming courses,
instructors and students may import the \texttt{davos} library into
their notebooks to provide a simple means of ensuring their code will
run on others' machines. When combined with online notebook-based
platforms like Google Colaboratory, \texttt{davos} provides a
convenient way to manage dependencies within a notebook, without
requiring any software (beyond a web browser) to be installed on the
students' or instructors' systems. For the same reasons,
\texttt{davos} also provides an elegant means of sharing ready-to-run
notebook-based demonstrations that install their dependencies
automatically.

@@

Our work also has several more subtle ``advanced'' use cases and
potential impacts. Whereas Python's built-in \texttt{import}
statement is agnostic to packages' version numbers, \texttt{smuggle}
statements (when combined with onion comments) are version-sensitive.
And because onion comments are parsed at runtime, required package and
their specified versions are installed in a just-in-time manner. Thus, it is possible
in most cases to \texttt{smuggle} a specific package version or revision even if
a different version has already been loaded. This enables more complex uses
that take advantage of multiple versions of a package within a single interpreter
session. This could be useful in cases where specific features are added or
removed from a package across different versions, or in comparing the
performance or functionality of particular features across different versions of
the same package.

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/flow_chart}
\caption{\small \textbf{\texttt{smuggle()} function logic.} }
\label{fig:flow-chart}
\end{figure}

@@

Like virtual environments, containers, and virtual machines, the
\texttt{davos} library (when used in conjunction with Jupyter
notebooks) provides a light\-weight mechanism for sharing code and
ensuring reproducibility across users and computing environments
(Fig.~\ref{fig:code-sharing}). Further, \texttt{davos} enables users
to fully specify (and install, as needed) any project dependencies
within the same notebook. This provides a system whereby executable
code (along with text and media) \textit{and} code for setting up and
configuring the project dependencies, may be combined within a single
notebook file.

We designed \texttt{davos} for use in research applications. For
example, in many settings, \texttt{davos} may be used as a drop-in
replacement for more-difficult-to-set-up virtual environments,
containers, and/or virtual machines. For researchers, this lowers
barriers to both sharing code. By eliminating most of the setup costs
of reconstructing the original researchers' computing environment,
\texttt{davos} also lowers barriers to entry for members of
the scientific community and the public who seek to benefit
from shared code.

Beyond research applications, \texttt{davos} is also useful in
pedagogical settings. For example, in programming courses,
instructors and students may import the \texttt{davos} library into
their notebooks to provide a simple means of ensuring their code will
run on others' machines. When combined with online notebook-based
platforms like Google Colaboratory, \texttt{davos} provides a
convenient way to manage dependencies within a notebook, without
requiring any software (beyond a web browser) to be installed on the
students' or instructors' systems. For the same reasons,
\texttt{davos} also provides an elegant means of sharing ready-to-run
notebook-based demonstrations or tutorials that install their dependencies
automatically.

@@

Our work also has several more subtle ``advanced'' use cases and
potential impacts. Whereas Python's built-in \texttt{import}
statement is agnostic to packages' version information, \texttt{smuggle}
statements (when combined with onion comments) are version-sensitive.
And because onion comments are parsed at runtime, required packages and
their specified versions are installed in a just-in-time manner. Thus, it is possible
in most cases to \texttt{smuggle} a specific package version or revision even if
a different version has already been loaded. This enables more complex uses
that take advantage of multiple versions of a package within a single interpreter
session. This could be useful in cases where specific features are added or
removed from a package across different versions, or in comparing the
performance or functionality of particular features across different versions of
the same package.
